
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Expectations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Communication:} Students are expected to consult their emails and blackboard messages \textit{at least} twice a week, and to answer these as relevant. 

\paragraph{Class and Lab Participation:} Keeping up with class contents and participation in both lecture and lab sessions are critical factors of your success in this course. 

\textit{Students should be on time for all scheduled sessions and attend the entire session.} 
%Attendance will be taken at every synchronous class and lab session and will count towards your class participation grade. 
This semester attendance will not be taken to discourage those who may be sick to stay home, 
but those students who attend and readily participate in the course do better on assessments.

Students should notify the instructor prior to missing a session if at all possible, and certainly right after if earlier was not possible. 
%The instructor will allow two unexcused absences per semester before having the option to deduct points from the final grade (5 points per subsequent unexcused absence). 
Students should submit their work on time and meet all deadlines. Failing to do so will affect the participation grade.


\textit{It is the student's responsibility to review the content covered during missed class(es) or labs, as well as the assignments given during their absence.}
Participation points also include completing post-lecture and post-labs online quizzes (when requested) that are administered as surveys to monitor students’ overall progress and potential struggles.

\textit{Students should be on task.} 
When in synchronous class or lab session, students are expected to direct their attention to the task / activity as directed by the lecture / lab instructor. 
For instance, synchronous class sessions are certainly not places for social-networking, working on homework, participating in other courses.

\textit{Professionalism:} 
Students should be professional in their communications, as the context permits.
Emails should contains subjects, the recipients should be addressed (i.e. ``Hello Dr. DeBlasio, ...''), and the email should be signed with your name. 
Real-time online communication (i.e. MS Teams), while less formal, should still be professional. 
