
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Standing in the course}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Standing in the Course:} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Students will have access to their grades for all assignments so that they can self-monitor their standing and progress. 
However, it is also completely fine for any student to come and talk to their instructor about their standing and work together to make sure the student is as successful as can be.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Dropping the Course:} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Every semester, some students drop the course. We, instructors, completely understand and respect that. We only hereby ask students to inform us, ideally before, but in the worst-case right after, of their intention to drop the course. This is really important for us as it possibly informs us of ways in which to better serve our students.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Special notices for COVID-19}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Please stay home if you have been diagnosed with COVID-19 or are experiencing COVID-19 symptoms. 
If you are feeling unwell, please let me know as soon as possible, so that we can work on appropriate accommodations. 
If you have tested positive for COVID-19, 
you are encouraged to report your results to covidaction@utep.edu, 
so that the Dean of Students Office can provide you with support and help with communication with your professors. 
The Student Health Center is equipped to provide COVID-19 testing. 
 
The Center for Disease Control and Prevention recommends that people 
in areas of substantial or high COVID-19 transmission wear face masks when indoors in groups of people. 
The best way that Miners can take care of Miners is to get the vaccine. 
If you still need the vaccine, it is widely available in the El Paso area, 
and will be available at no charge on campus during the first week of classes. 
For more information about the current rates, testing, and vaccinations, please visit epstrong.org.

\begin{tcolorbox}[colback=red!5,colframe=red!75!black,title=Masks in the classroom]
The instructional staff will be following CDC guidance on masking in groups based on the current transmission rates in El Paso Country\footnote{\url{https://www.cdc.gov/coronavirus/2019-ncov/your-health/covid-by-county.html}}. 
Please respect the choices of other who may prefer to be more cautious than recommendations. 
\end{tcolorbox}

%While there is not a plan to hold any meetings of 2401 on campus this semester, 
%as the university updates it's campus operations there may be situations that lead a student to be on campus. 
%The following are a summary of the universities policies regarding COVID-19.
%
%You must STAY OFF CAMPUS and REPORT if you:
%(1) have been diagnosed with COVID- 19, 
%(2) are experiencing COVID-19 symptoms, or 
%(3) have had recent contact with a person who has received a positive coronavirus test. 
%Reports should be made at \href{http://screening.utep.edu}{\texttt{screening.utep.edu}}. 
%If you know anyone who should report any of these three criteria, encourage them to report. 
%If the individual cannot report, you can report on their behalf by sending an email to \url{COVIDaction@utep.edu}.
%
%For each day that you attend campus—for any reason—you must complete the questions on the UTEP screening website (\href{http://screening.utep.edu}{\texttt{screening.utep.edu}}) prior to arriving on campus. 
%The website will verify if you are permitted to come to campus. 
%Under no circumstances should anyone come to class when feeling ill or exhibiting any of the known COVID-19 symptoms. 
%If you are feeling unwell, please let me know as soon as possible, 
%and alternative instruction will be provided. Students are advised to minimize the number of encounters with others to avoid infection.
%
%Wear face coverings when in common areas of campus or when others are present. 
%You must wear a face covering over your nose and mouth at all times in this class. 
%If you choose not to wear a face covering, you may not enter the classroom. 
%If you remove your face covering, you will be asked to put it on or leave the classroom. 
%Students who refuse to wear a face covering and follow preventive COVID-19 guidelines will be dismissed from the class and will be subject to disciplinary action according to Section 1.2.3 Health and Safety and Section 1.2.2.5 Disruptions in the UTEP Handbook of Operating Procedures.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Resources}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Special Accommodations: }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
If you have a disability and need classroom accommodations, please contact the Center for Accommodations and Support Services (CASS) at 747-5148 or by email to cass@utep.edu, or visit their office located in UTEP Union East, Room 106. For additional information, please visit the CASS website at \href{http://www.sa.utep.edu/cass}{\texttt{www.sa.utep.edu/cass}}. CASS’ staff are the only individuals who can validate and if need be, authorize accommodations for students with disabilities.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Scholastic Dishonesty: }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Any student who commits an act of scholastic dishonesty is subject to discipline. Scholastic dishonesty includes, but not limited to cheating, plagiarism, collusion, and submission for credit of any work or materials that are attributable to another person.

Cheating is:
\begin{itemize}
\item Copying from the test paper of another student
\item Communicating with another student during a test to be taken individually
\item Giving or seeking aid from another student during a test to be taken individually
\item Possession and/or use of unauthorized materials during tests (i.e. crib notes, class notes, books, etc.)
\item Substituting for another person to take a test
\item Falsifying research data, reports, academic work offered for credit
\end{itemize}

Plagiarism is:
\begin{itemize}
\item Using someone’s work in your assignments without the proper citations
\item Submitting the same paper or assignment from a different course, without direct permission of instructors
\item[]\vspace{1em} To avoid plagiarism, see: \\{\footnotesize\url{https://www.utep.edu/student-affairs/osccr/_Files/docs/Avoiding-Plagiarism.pdf}}
\end{itemize}
                               
Collusion is:
\begin{itemize}
\item Unauthorized collaboration with another person in preparing academic assignments
\end{itemize}

\begin{tcolorbox}[colback=red!5,colframe=red!75!black,title=Important!]
When in doubt on any of the above, please contact your instructor to check if you are following authorized procedure. Also, please check the UTEP’s Handbook of Operating Procedures at: hoop.utep.edu. 
\end{tcolorbox}

