\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage[margin=1in]{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{awesomebox}
%SetFonts

%SetFonts

\usepackage{amsmath}
\DeclareMathOperator{\plainmod}{\text{ mod }}
\let\emptyset\varnothing

\newcommand{\reals}{\mathbb{R}}
\newcommand{\realsText}{$\mathbb{R}$}
\newcommand{\ints}{\mathbb{Z}}
\newcommand{\intsText}{$\mathbb{Z}$}

\title{Homework 8}
\author{Discrete Structures 1}
\date{due: 4 May 2023, 8:00am}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

Your task for this homework will be to answer the following questions without using any calculating resources. 
Your responses should be submitted via blackboard by the due date above as a PDF (submissions in any other format will be returned to the user and a resubmissions will be requested). 
You are free to use whatever tools you would like to generate the response document: 
scanned hand-written paper, 
tablet generated hand-written, 
microsoft word (with this option, please use the equation editor to correctly format your responses), 
\LaTeX, etc.
Your TA, IA, and Instructor are available to help during their designated office hours or via email 
(note that emails sent during non-business hours may not be responded to until the next working day). 

%\importantbox{
%\textbf{Note:} all of these questions are on topics from chapters 5; thus you will only be proving by induction in this homework assignment. 
%}
\begin{enumerate}
% 2.61
\item What is the smallest positive integer $n$, where $n\bmod 2=0$, $n\bmod3=0$, and $n\bmod5=0$?

%2.85
\item Compute the following nested sum (and show each step): $\displaystyle \sum_{i=1}^4\sum_{j=i}^4 \left(j^i\right)$


%2.137
\item What is the power set of$\{1,a\}$?

\item 
Given the vectors $v = \langle \sqrt{2}, 5\rangle$ and $w = \langle \sqrt{2}, 12\rangle$, 
is $v \cdot w$ rational or irrational? 
(note this is the dot product not multiplication since $v$ and $w$ are vectors.)

%2.147
\item Let $S = \{1,2,3,4,5,6,7,8\}$, and let $T$ be an unknown set.
suppose that $S\times T=\emptyset$.
What can you conclude about $T$?

%2.251
\item Let $f(x)=3x+1$ and let $g(x)=2x$. 
Identify a function $h$ such that $g\circ h$ and $f$ are identical.
(For example, the function $f \circ g$ is given by the definition $(f \circ g)(x) = f(g(x)) = 6x + 1$.)

%2.269
\item Consider $f:\mathbb{R}\rightarrow\mathbb{R}$, where $f(x)=3x+1$.
What is the inverse of $f$?

%4.95
\item For the following false claim and a bogus proof of that false claim 
(a) identify the precise error in the proof, and 
(b) give a counterexample to the claim. 
(Note that saying why the claim is false does not address (a) in the slightest—it would be possible to give a bogus proof of a true claim!)

\textbf{False Claim 1.} 
Let $n$ be a positive integer and let $p, q \in \ints^{\ge2}$ , where $p$ and $q$ are prime. 
If $n$ is evenly divisible by
both $p$ and $q$, then $n$ is also evenly divisible by $pq$.

\textbf{Bogus proof.} 
Because $p | n$, there exists a positive integer $k$ such that $n = pk$. 
Thus, by assumption, we know that $q | pk$. 
Because $p$ and $q$ are both prime, 
we know that $p$ does not evenly divide $q$, and thus the only way that $q | pk$ can hold is if $q | k$. 
Hence $k = q\ell$ for some positive integer $\ell$, and thus $n = pk = pq\ell$. 
Therefore $pq | n$.


\end{enumerate}
\end{document}