\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage[margin=1in]{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts

\usepackage{amsmath}
%\DeclareMathOperator{\mod}{mod}

\title{Homework 2}
\author{Discrete Structures 1}
\date{due: 14 February 2023, 8:00am}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

Your task for this homework will be to answer the following questions without using any calculating resources. 
Your responses should be submitted via blackboard by the due date above as a PDF (submissions in any other format will be returned to the user and a resubmissions will be requested). 
You are free to use whatever tools you would like to generate the response document: 
scanned hand-written paper, 
tablet generated hand-written, 
microsoft word (with this option, please use the equation editor to correctly format your responses), 
\LaTeX, etc.
Your TA, IA, and Instructor are available to help during their designated office hours or via email 
(note that emails sent during non-business hours may not be responded to until the next working day). 

\begin{enumerate}
%2.91
\item Let $S=\left\{\left(0+0\right), \left(0+1\right), \left(1+0\right), \left(1+1\right), \left(0\cdot0\right), \left(0\cdot1\right), \left(1\cdot0\right), \left(1\cdot1\right)\right\} $, what is $|S|$?
%2.92&93
\item Let $T = \left\{n \in\mathbb{Z} : 0\le n \le 20 \text{ and } n \mod 2 = n \mod 3\right\}$ 
and \\$H = \left\{0,1,2,3,4,5,6,7,8,9,a,b,c,d,e,f\right\}$. 
Identify at least one element of $H$ that is not an element of $T$, and 
at least one element of $T$ that is not an element of $H$
%2.97
\item Rewrite the following set by exhaustively listing its elements: \\$\left\{n\in\mathbb{Z} :0\le n\le 20 \text{ and } n\mod5=n\mod7\right\}$.
%2.108
\item In general, $A-B$ and $B-A$ do \textit{not} denote the same set.
%(SeeFigure2.19d.)
But your friends Evan and Yasmin wander by and tell you the following. 
Let $E$ denote the set of CS homework questions that Evan has not yet solved. 
Let $Y$ denote the set of CS homework questions that Yasmin has not yet solved. 
Evan and Yasmin claim that $E-Y = Y-E$. 
Is this possible? If so, under what circumstances? If not, why not? Justify your answer.

%2.114-2.117
\item Let $F = \{1,2,4,8\}$, $G = \{1,3,9\}$, and $H = \{0,5,6,7\}$. 
Where relevant, let \\$U = \{n\in\mathbb{Z} :0\le n\le 9\}$ be the universe.
\begin{enumerate}
\item Are $F$ and $G$ disjoint?
\item Are $G$ and $\overline F$ ($\sim F$) disjoint?
\item Are $F\cap G$ and $H$ disjoint?
\item Are $H$ and $\overline H$ disjoint?
\end{enumerate}


%2.136
\item Define $S=\left\{x\in \mathbb{Z}: x \in \left[1,100\right]\right\}$.
Let $W=\left\{x \in S: x \bmod 2 = 0\right\}$, $H=\left\{x \in S:x \mod 3=0\right\}$, and $O=S-H-W$.
Is $\left\{W,H,O\right\}$ a partition of $S$?
%2.137
\item What is the power set of$\{1,a\}$?
%2.147
\item Let $S = \{1,2,3,4,5,6,7,8\}$, and let $T$ be an unknown set.
suppose that $S\times T=\emptyset$.
What can you conclude about $T$?
\end{enumerate}

\end{document}