\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage[margin=1in]{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts

\usepackage{amsmath}
%\DeclareMathOperator{\mod}{mod}

\title{Homework 1}
\author{Discrete Structures 1}
\date{due: 7 February 2023, 8:00am}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

Your task for this homework will be to answer the following questions without using any calculating resources. 
Your responses should be submitted via blackboard by the due date above as a PDF (submissions in any other format will be returned to the user and a resubmissions will be requested). 
You are free to use whatever tools you would like to generate the response document: 
scanned hand-written paper, 
tablet generated hand-written, 
microsoft word (with this option, please use the equation editor to correctly format your responses), 
\LaTeX, etc.
Your TA, IA, and Instructor are available to help during their designated office hours or via email 
(note that emails sent during non-business hours may not be responded to until the next working day). 

\begin{enumerate}
%2.5
\item If $x$ and $y$ are integers, is $x+y$ necessarily an integer? Why or why not? 
%2.6
\item If $x$ and $y$ are rationals, is $x+y$ necessarily an rational? Why or why not? 
%2.10
\item What is the value of $\left(\left\lfloor3.14159\right\rfloor\right)^{\left\lceil3.14159\right\rceil}$?
%2.22
\item Are $\left\lfloor\left| x \right|\right\rfloor$ and $\left|\left\lfloor x \right\rfloor\right|$ always equal? Why or why not?
%2.40
\item Without using a computer or calculator decide which is bigger: $\log_{10}17$ or $\log_{17}10$? \\(show each step used to make the decision)
% 2.61
\item What is the smallest positive integer $n$, where $n\bmod 2=0$, $n\bmod3=0$, and $n\bmod5=0$?
%2.64
\item What is the smallest positive integer $n$ where $n \bmod3=2$, $n \bmod5=3$, and $n \bmod 7=5$?
%2.71
\item Compute the following sum (and show each step): $\displaystyle \sum_{i=1}^{6}2^{2i}$
%2.67
\item Compute the following product (and show each step): $\displaystyle \prod_{i=1}^{6}2^{2i}$
%2.85
\item Compute the following nested sum (and show each step): $\displaystyle \sum_{i=1}^4\sum_{j=i}^4 \left(j^i\right)$
\end{enumerate}

\end{document}