\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage[margin=1in]{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{awesomebox}
%SetFonts

%SetFonts

\usepackage{amsmath}
%\DeclareMathOperator{\mod}{mod}
\let\emptyset\varnothing

\newcommand{\reals}{\mathbb{R}}
\newcommand{\realsText}{$\mathbb{R}$}
\newcommand{\ints}{\mathbb{Z}}
\newcommand{\intsText}{$\mathbb{Z}$}

\title{Homework 4}
\author{Discrete Structures 2}
\date{due: 30 March 2023, 8:00am}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

Your task for this homework will be to answer the following questions without using any calculating resources. 
Your responses should be submitted via blackboard by the due date above as a PDF (submissions in any other format will be returned to the user and a resubmissions will be requested). 
You are free to use whatever tools you would like to generate the response document: 
scanned hand-written paper, 
tablet generated hand-written, 
microsoft word (with this option, please use the equation editor to correctly format your responses), 
\LaTeX, etc.
Your TA, IA, and Instructor are available to help during their designated office hours or via email 
(note that emails sent during non-business hours may not be responded to until the next working day). 

%\importantbox{
%\textbf{Note:} all of these questions are on topics from chapters 5; thus you will only be proving by induction in this homework assignment. 
%}
\begin{enumerate}

\item Complete the proof below:
We will prove by \textit{weak} induction on $n$ that \[\sum_{i=1}^{n}f_i = f_{n+2}-1\] (where $f_k$ is the $k$-th fibonacci number). 

\textbf{Base cases} ($n=1$ and $n=2$):
 \[\sum_{i=1}^{1}f_i = f_1 = 1 = 2 - 1 = f_{3}-1\] and
 \[\sum_{i=1}^{2}f_i = f_1 + f_2 = 1 + 1 = 2 = 3 - 1 = f_{4}-1.\]
 
\textbf{Inductive case} ($n\ge 3$):\\
\hspace*{3em}We will assume the inductive hypothesis holds for $n-1$, that is $\sum_{i=1}^{n-1}f_i = f_{n+1}-1$. \\
\hspace*{3em} (note you will likely use direct prove to complete the rest of the inductive case,\\ 
\hspace*{3em} remember to start with the original proposition)

\item A string over an alphabet $\Sigma$ is a sequence of elements of a set --- that is, a string $x$ over $\Sigma$ satisfies $x \in \Sigma^n$ for some length $n\ge 0$.
How many strings of length \textit{at most} $n$ over the alphabet $\Sigma = \{\texttt{A},\texttt{B},...,\texttt{Z},\text{\textvisiblespace}\}$ are there? 
How many contain exactly 2 ``words'' (that is they contain exactly one space and its not in the first or last position). 

\clearpage
\item Define a palindrome bit string as one that satisfies one of the following conditions: 
\begin{itemize}
\item the empty string (containing no bits);
\item the string \texttt{0};
\item the string \texttt{1};
\item the string \texttt{0x0} where \texttt{x} is a palindrome bit string; or 
\item the string \texttt{1x1} where \texttt{x} is a palindrome bit string.
\end{itemize}
Further define $\#0(s)$ and $\#1(s)$ to be the number of \texttt{0}s and \texttt{1}s respectively in a string $s$.

Prove by \textbf{structural induction}, that is induction not over the string $s$, that the proposition $P$ holds for all palindrome bit strings $s$:
\[ P(s):\text{ the value of }[\#0(s)] \cdot [\#1(s)]\text{ is even} \]
(note that the two numbers are multiplied not summed).

\tipbox{The structure of your proof will likely be on the cases in the definition of palindrome bit strings, notice some cases rely on others}

\end{enumerate}

\end{document}