\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage[margin=0.75in]{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts

\usepackage{amsmath}
%\DeclareMathOperator{\mod}{mod}

\let\emptyset\varnothing

\newcommand{\reals}{\mathbb{R}}
\newcommand{\realsText}{$\mathbb{R}$}
\newcommand{\ints}{\mathbb{Z}}
\newcommand{\intsText}{$\mathbb{Z}$}
\renewcommand{\mod}{\ \mathrm{mod}\ }


\title{Midterm Exam}
\author{Discrete Structures 1}
\date{9 March 2023, \textbf{12noon}}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}
\begin{center}
Name: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\(please write legibly) 
\end{center}

\begin{center}
\begin{tabular}{|c|l|l|}
\hline
\textbf{Question} & \multicolumn{1}{|c|}{\textbf{Topic}} & \multicolumn{1}{|c|}{\textbf{Value}}\\
\hline
\hline
1 & (modulus) & \hspace{3em}/20\\ \hline
2 & (modulus) & \hspace{3em}/20\\ \hline
3 & (sums/products) & \hspace{3em}/90\\ \hline
4 & (sets) & \hspace{3em}/90\\ \hline
5 & (sets) &  \hspace{3em}/40\\ \hline
6 & (vectors) & \hspace{3em}/90\\ \hline
7 & (logic) & \hspace{3em}/120\\ \hline
 & \textbf{bonus} &\\ \hline
 \hline
\hline
\multicolumn{2}{|l|}{\textbf{Total}} & \hspace{4em}/470\\
\hline
\end{tabular}
\end{center}


\textbf{\underline{There are a few rules:}}

(1) You are not allowed to use outside online resources. 
No outside help (e.g., from a classmate, a friend, online search, documents on your own laptop, etc.) will be tolerated. 
Any attempt to obtain help or information about the exam will be reported.

(2) \textbf{You are not allowed to use headphones during the exam.} Your phone should be in your backpack.

(3) You should only have a pencil, an eraser, and a pencil sharpener with you on the table at the time of the exam. 
Everything else should be safely packed in your backpack and not to be used at any time during the exam.

(4) You were told to attend to the bathroom before the exam starts: 
you will not be allowed to leave the room during the first hour of the exam (unless you have a doctor’s note to indicate otherwise).

\textbf{\underline{A few pieces of advice:}}

(1) Read the questions carefully and try the tracing exercises on draft paper before you answer on your exam copy.

(2) Pay careful attention to the instructions written in the exam.

\textbf{\underline{Please write legibly and in a structured manner:}} 
keep in mind that what you write needs to be read. Answers that are unreadable or hard to follow will not receive full credit.




\clearpage

\begin{enumerate}


\item
For a given $x\in\mathbb{Z}^{\ge1}$, what is minimum value of \underline{$x\mod 19$}? What is the maximum? 
\vspace{3em}

\item 
For a given $b\in\mathbb{Z}^{\ge1}$ and $a \in\mathbb{Z}^{\ge b}$, what is the relationship between the values of \underline{$a\mod b$} and \underline{$(a - b) \mod b$}?
\vspace{3em}

\item Write the equation represented by the following (that is, do not give a single number, write out all of the terms):
\begin{enumerate}
\item $\displaystyle\prod_{i=1}^{6} i^3$\vspace{2em}
\item $\displaystyle\sum_{i=1}^{4} i^{-2}$\vspace{2em}
\item $\displaystyle\sum_{i=1}^{4}\sum_{j=i}^{3} (i \cdot j)$\vspace{2em}
\end{enumerate}

\item 
Let $A = \left\{0,1,3,4,5,7,8,9\right\}$, $B = \left\{0,4,5,9\right\}$, and $C = \left\{0,3,6,9\right\}$.
\begin{enumerate}
\item What is $A\cap B$? \vspace{2em}
\item What is $B\cup C$? \vspace{2em}
\item What is $|B\cup C|$? \vspace{2em}
\item What is $C-B$? \vspace{2em}
\item Is $A \subseteq B$?\vspace{2em}
\item Is $A \supseteq B$?\vspace{2em}

\end{enumerate}


\item True or false: $6 \in \left\{k \in \mathbb{Z}^{\ge1} : k^2 \le 10\right\}$? Explain your response. \vspace{3em}

\clearpage
\item For the vectors $a=\langle2,-2\rangle$ and $b=\langle 1,3 \rangle$:
\begin{enumerate}
\item What is $a\cdot b$? \vspace{2em}
\item What is $a\cdot a$? \vspace{2em}
\item What is $b-a$? \vspace{2em}
\end{enumerate}

\item Fill in the following truth table on two atomic propositions $p$ and $q$, then answer the question below:\\
\begin{center}
\begin{tabular}{c|c||c|c|c|c|c}
$p$ & $q$ & $\neg p$ & $\neg q$ & $q \wedge p$ & $\neg (p \wedge q)$ & $\neg p \vee \neg q$\\
\hline
\hline
\hspace*{2em}& \hspace{2em} & \hspace{2em} & \hspace{2em} & \hspace{2em} & \hspace{2em} & \hspace{2em} \\
& & & & & &\\& & & & & &\\& & & & & &\\& & & & & &\\& & & & & &\\& & & & & &\\
\end{tabular}
\end{center}

Are $\neg (p \wedge q)$ and $\neg p \vee \neg q$ equivalent? Explain your answer.\vspace{4em}

\item BONUS: 
\begin{enumerate}
\item $|\ints|=$
\item $|\mathbb{Q}|=$
\item $|\reals|=$
\item True or False: $|\ints| = |\reals|$
\item True or False: $|\mathbb{Q}| \le |\reals|$
\end{enumerate}

\end{enumerate}

\end{document} 